\subsubsection{Application and refinement of the model} \ \\*[0.5\baselineskip]
  Moving on to future plans for the research on payment channels, first and foremost we
  want to experiment with the model presented in Subsection~\ref{sec:channels}. In
  particular, it is of great importance to ascertain whether the various existing concrete
  designs can be expressed in terms of our model. We will start by transcribing the
  simplest payment channel design, the Lightning Network~\cite{lightning}, and gradually
  make our way to more complex systems. We will alter and improve our model so as to
  accommodate for as many systems as possible. If serious hurdles are encountered in the
  process, we will attempt to formally argue on the reasons and produce relevant
  impossibility results. We may need to create two or more incompatible models to account
  for various incompatible situations.

  A direction that has not been taken as of yet by any of the proposed systems (to our
  knowledge) is to make some trust assumptions in order to build a more robust, cheaper
  system. Even though trustless off-chain payments are certainly a useful feature, the
  lack of trust can be seen as a constraint. For example, it is plausible to consider
  channels where in case of unilateral settlement, an external, pre-agreed arbiter could
  have the final say on who receives which funds. This could obviate the need for long
  timeouts before the funds are unlocked for on-chain use but would entail some limited
  trust to the arbiter.

  An example of a payment channel where trust is involved in a simple (and easily
  exploitable) manner is the Lightning Network construction but with a 1-of-2
  multisignature~\cite{multisig} funding transaction instead of a normal 2-of-2
  transaction (more on this in Section~\ref{sec:literaturereview}). Our model should be
  capable of expressing such naive systems as well.

  We hope to have completed developing and fine-tuning our model in the span of the
  following 3-4 months, i.e. until the end of September 2018.
