\subsubsection{Trust and Reputation} \ \\*[0.5\baselineskip]
  Webs-of-trust can be used as a basis for trust as shown by Caronni \cite{wot}. PGP
  \cite{pgp} implements one and Pathfinder \cite{pathfinder} explores its transitive
  closure. Freenet \cite{freenet} implements a transitive web-of-trust for fighting spam.
  Mui et al. \cite{mui} and J\o{}sang et al. \cite{beta} propose ways of calculating trust
  towards distant nodes.  Vi\c{s}an et al. \cite{vpc} calculate trust in a hierarchical
  way. CA- and Byzantine-based \cite{byzantine} PKIs \cite{pki} and Bazaar \cite{bazaar}
  require central trusted third parties or at least authenticated membership. FIRE
  \cite{fire}, CORE \cite{core}, Gr\"unert et al. \cite{ghkkw} and Repantis et al.
  \cite{rk} do not prove any Sybil resilience. All these systems define trust in a
  non-financial manner.

  We agree with Gollmann \cite{badtrust} in that the meaning of trust should not be
  extrapolated. When formally defining trust, we will keep in mind their advice.

  Beaver \cite{beaver} includes a trust model that, to discourage Sybil attacks, relies on
  fees, something we would like to avoid. Our motivating application for exploring trust
  in a decentralized setting is OpenBazaar, where transitive financial trust has
  previously been explored by Zindros \cite{dionyziz}. That work however does not define
  trust as a monetary value. We are strongly inspired by Karlan et al. \cite{kmrs} who
  give a perceptive sociological approach to the connection between trust and risk.
  TrustDavis \cite{davis} proposes a financial trust system with transitivity and in which
  trust is defined as lines-of-credit.

  The work of Fugger \cite{iou}, applied in Ripple \cite{ripple} and Stellar
  \cite{stellar}, leverages the concept of money-as-debt. This approach is complementary
  to that of Trust is Risk~\cite{trustisrisk}, where a functionally similar construction
  defines trust-as-risk. We are currently experimenting with using the latter work as a
  concrete instantiation of $\mathcal{F}_{\mathrm{Trust}}$.
