\subsection{Decentralised E-Commerce}
  Going in more detail, blockchains provide us with novel capabilities. It is possible to
  immutably and truthfully record the fact that Alice paid Bob some cryptographic coins on
  a blockchain; it is possible for Bob to provably and irrefutably give her a digital
  asset in return (e.g. an ICO~\cite{eos}, or a sword in a future blockchain--backed game)
  and record the fact on a blockchain as well; additionally, it is possible to make the
  exchange atomic so that no trust between the two parties is needed. Unfortunately, all
  the above are impossible to accomplish if the asset is physical. Alice may pay first and
  then Bob can refuse to give the asset; or Bob may indeed hand in the asset, but Alice
  may then claim that it was not as advertised and demand her money back. The possibility
  of fraud is exacerbated if the exhange takes place online between parties who do not
  know each other personally. Crucially, an external observer cannot always resolutely
  decide which of the parties is right. Even if she can, it seems difficult for her to
  prove that she is not colluding with either player and that she is completely fair and
  impartial, since her background, objectives and affiliations are seldom entirely
  transparent to both parties.

  For comparison, if the payment is done in fiat currency, then there exists a mediator
  (usually a bank, often a court) who is charged with deciding what is the fair way to
  settle the dispute. Additionally, it is in the mediator's direct benefit to strive for
  the objectively fairest solution. Unfortunately, from a cryptographic point of view,
  such an assumption is too strong: it is entirely possible that the bank employee or the
  judge who has the final say is a friend of the fraudster. Nevertheless, it seems that
  currently the incentives are much better aligned when relying on the traditional legal
  system. As a result, transacting in fiat currency is, for practical and everyday
  purchases of physical goods and especially in the online setting, safer and more robust
  than using cryptocurrencies.

  The cryptographic achievements of blockchains are currently realised only in a closed
  system, where everything can be proven mathematically. Nevertheless, the economy is not
  a closed system: New resources can be found, rules, conventions and legislations can be
  changed, groundbreaking inventions change the landscape of the market rapidly and the
  desires of consumers evolve. In order for decentralised blockchains to substitute the
  traditional fiat currencies, a mechanism for decentralised e-commerce with guarantees of
  minimal trust is needed. We propose to attempt the creation of such a mechanism or give
  plausible arguments why such a mechanism is unattainable. In case we manage to create
  such a system, we should ideally be able to construct the backend of a decentralised
  ecommerce platform, similar in usage to existing platforms such as
  OpenBazaar~\cite{openbazaar}.

  In essence, such a mechanism would provide a decentralised reputation system. In current
  online marketplaces (e.g. ebay.com) there exists a central authority that aggregates
  ratings and reviews from past interactions between users and serves them to participants
  of future transactions with the aim of minimising fraud. We aspire to replace this
  central authority with a distributed protocol or prove that such an endeavour is
  impossible.
